Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-08-06 pot/LaTeX/jsm2014.tex
typo bounds
forgot to scale covariates

\begin{frame}{Example daily partition}
	Two sample partitions (number is at partition center)
    \centering
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-1.pdf}
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-2.pdf}
\end{frame}

\begin{frame}{Simulated $\chi$ plots}
  \centering
  \includegraphics[width=1\linewidth]{./plots/chi-plots.pdf}\\[-0.25in]
  \includegraphics[width=0.2\linewidth]{./plots/chi-legend.pdf}
\end{frame}

\begin{frame}{Sample simulated datasets}
  \centering
  \includegraphics[width=1\linewidth]{./plots/gauss-vs-skew-t3.pdf}
\end{frame}

@@

\begin{frame}{Data analysis}
	\centering
	Ozone monitoring station locations
    \includegraphics[width=0.8\linewidth]{./plots/ozone_station.pdf}

@@

\begin{frame}{Data analysis}
  \centering
  Max 8-hour ozone measurements at 85 sites in NC, SC, and GA for days 5 and 34.
    \includegraphics[width=1\linewidth]{./plots/ozone-day.pdf}

@@

\begin{frame}{Exploratory data analysis}
	\centering
	$\chi$-plot for residuals selected ozone sample quantiles
    \includegraphics[width=1\linewidth]{./plots/chi-plot-ozone-res.pdf}
\end{frame}

\begin{frame}{Model comparisons}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 9 different analysis methods incorporating
    \begin{itemize}
      \item Gaussian vs $t$ vs skew-$t$ marginal distribution
      \item $K=1$ partition vs $K=5$ partitions
      \item No thresholding vs thresholding at $T=0.90$ sample quantile
    \end{itemize}
    \item All methods use a \Matern or exponential covariance ($\nu = 0.5$)
    \item Compare quantile and Brier scores using 5-fold cross validation (Gneiting and Raftery, 2007)
    \item Mean function modeled using a first-order spatial trend
  \end{itemize}
\end{frame}

@@

\begin{frame}{Five-fold cross-validation results}
  \begin{table}[htbp]
    \small
    \centering
    \begin{tabular}{l|c|r|rrrrr}
          \multicolumn{3}{c}{\ } & \multicolumn{5}{c}{Quantile}\\
           \hline
  Marginal & $K$ & $T$  & 0.900 & 0.950 & 0.990 & 0.995 & 0.999\\
  \hline
Gaussian & 1 & 0 & 16.38 & 15.76 & 14.52 & 14.08 & 13.22\\
$t$ & 1 & 0 & 16.15 & 15.51 & 14.00 & 13.43 & 12.32\\
$t$ & 5 & 0 & 13.61 & 12.66 & 10.96 & 10.40 & 9.34\\
skew $t$ & 1 & 0 & 9.24  & 7.27 & 4.13  & 3.27  & 1.96\\
skew $t$ & 5 & 0 & 15.81 & 14.46 & 11.57 & 10.57 & 8.60\\
$t$ & 1 & 0.9 & 5.52  & 3.58  & 1.77  & 1.47  & 1.10\\
$t$ & 5 & 0.9 & 5.98  & 4.27  & 2.41  & 2.03  & 1.49\\
 skew $t$ & 1 & 0.9 & {\bf 4.91}  & {\bf 3.16} & {\bf 1.45}  & {\bf 1.16}  & {\bf 0.82}\\
skew $t$ & 3 & 0.9 & 5.58 & 3.78 & 1.93& 1.58& 1.11\\
\hline
    \end{tabular}
  \end{table}
  \begin{itemize}
  	\item Brier score results are similar.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Example daily partition}
    \centering
    \begin{figure}
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-1.pdf}
    \includegraphics[width=0.54\linewidth]{./plots/example-partition-2.pdf}
    \caption{Two sample partitions (number is at partition center)}
    \end{figure}
\end{frame}

\begin{frame}{Simulated $\chi$ plots}
  \centering
  \begin{figure}
  \includegraphics[width=1\linewidth]{./plots/chi-plots.pdf}\\[-0.25in]
  \includegraphics[width=0.2\linewidth]{./plots/chi-legend.pdf}
  \caption{$\chi$ plots from simulated datasets}
  \end{figure}
\end{frame}

\begin{frame}{Sample simulated datasets}
  \centering
  \begin{figure}
  \includegraphics[width=1\linewidth]{./plots/gauss-vs-skew-t3.pdf}
  \caption{Gaussian and skew-$t$ with 3 partitions}
  \end{figure}
\end{frame}

@@

\begin{frame}{Data analysis}
	\centering
	\begin{figure}
    \includegraphics[width=0.8\linewidth]{./plots/ozone_station.pdf}
    \caption{Ozone monitoring station locations}
    \end{figure}

@@

\begin{frame}{Data analysis}
  \centering
  \begin{figure}
    \includegraphics[width=1\linewidth]{./plots/ozone-day.pdf}
    \caption{Max 8-hour ozone measurements at 85 sites in NC, SC, and GA for days 5 and 34.}
   \end{figure}

@@

\begin{frame}{Exploratory data analysis}
	\centering
  \begin{figure}
    \includegraphics[width=1\linewidth]{./plots/chi-plot-ozone-res.pdf}
    \caption{$\chi$-plot for residuals of ozone sample quantiles}
  \end{figure}
\end{frame}

\begin{frame}{Model comparisons}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 9 different analysis methods incorporating
    \begin{itemize}
      \item Gaussian vs $t$ vs skew-$t$ marginal distribution
      \item $K=1$ partition vs $K=3$ partitions
      \item No thresholding vs thresholding at $T=0.90$ sample quantile
    \end{itemize}
    \item All methods use a \Matern or exponential covariance ($\nu = 0.5$)
    \item Compare quantile and Brier scores using 5-fold cross validation (Gneiting and Raftery, 2007)
    \item Mean function modeled using a first-order spatial trend
  \end{itemize}
\end{frame}

@@

\begin{frame}{Five-fold cross-validation results}
  \begin{table}[htbp]
    \small
    \centering
    \begin{tabular}{l|c|r|rrrrr}
          \multicolumn{3}{c}{\ } & \multicolumn{5}{c}{Quantile}\\
           \hline
  Marginal & $K$ & $T$  & 0.900 & 0.950 & 0.990 & 0.995 & 0.999\\
  \hline
Gaussian & 1 & 0 & 3.807 & 2.981 & 1.797 & 1.493 & 1.044\\
$t$ & 1 & 0 & 2.622 & 1.584 & 0.436 & 0.244 & 0.063 \\
$t$ & 3 & 0 & 2.643 & 1.601 & 0.455 & 0.265 & 0.085 \\
skew-$t$ & 1 & 0 & 2.766 & 1.683 & 0.467 & 0.257 & 0.063 \\
$t$ & 1 & 0.9 & 4.514 & 2.422 & 0.577 & 0.318 & 0.086 \\
skew-$t$ & 1 & 0.9 & 4.396 & 2.388 & 0.573 & 0.311 & 0.079 \\
\hline
    \end{tabular}
    \caption{Selected five-fold cross-validation results}
  \end{table}
  \begin{itemize}
  	\item Results for 
  	\item Brier score results are similar.
  \end{itemize}
\end{frame}
